\begin{thebibliography}{99}
\bibitem{AnAH10}
Andriescu E.-M., Azzabi A., Hains G. Parallel 
processing of Forward XPath queries: an experiment 
with BSML, \emph{TR-LACL} Vol 11, 2010 
\bibitem{AvGT02}
Avila-Campillo I., Green T. J., et al. XMLTK: An
XML toolkit for scalable XML stream processing.
\emph{Technical report, PlanX}, 2002.
\bibitem{BLKK09}
Bordawekar, R., Lim, L., Kementsietsidis, A., Kok, 
B., To Parallelize or Not to Parallelize: XPath 
Queries on Multi-core Systems, \emph{IBM Research 
Report}, 2009 
\bibitem{CVZT02}
Chien S.Y., Vagena Z., Zhang D., Tsotras V. J., Zaniolo C.,Efficient 
Structural Joins on Indexed XML Documents. \emph{VLDB 2002}, pp.263--274, 2002,
\bibitem{DiFF11}
Diao Y., Fischer P., Franklin M., et al. YFilter:
Efficient and scalable filt. of XML doc. In ICDE,
pages 341--342, 2002.
\bibitem{EmIm12}
Emoto, K., Imachi, H.: Parallel tree reduction on {MapReduce}.
In \emph{Proceedings of the International Conference
  on Computational Science} (\emph{ICCS 2012}),
  \emph{Procedia Computer Science}, vol.~9, pp. 1827--1836. Elsevier, 2012.
\bibitem{xpathcategory}
Franceschet M., XPathMark: Functional and performance tests for XPath.
In \emph{XQuery Implementation Paradigms}, Dagstuhl Seminar Proceedings No. 06472, Internationales Begegnungs- und Forschungszentrum f{\"u}r Informatik (IBFI), Schloss Dagstuhl, Germany, 2007.
\bibitem{FrDa11}
Francis N., David C., and Libkin L., A direct
transation from XPath to nondet. automata. \emph{In
Workshop on Foundations of Data Management}, pp.350--361, 2011
\bibitem{mbridges1}
Gazit H., Miller G.L., Teng S.-H., Optimal tree contraction in EREW model, \emph{Proceedings of the Princeton Workshop on Algorithms, Architectures, and Technical Issues for Models of Concurrent Computation}, pp.139-156, 1987
\emph{APLAS}, 2002
\bibitem{Grus02}
Grust T., Accelerating XPath Location Steps. \emph{SIGMOD 2002}, pp.109--120, 2002
\bibitem{HSYW14}
Huang X., Si X., Yuan X., Wang C., A Dynamic 
Load-balancing Scheme for XPath Queries Parallelization 
in Shared Memory Multi-core Systems, 
\emph{Journal of Computers}, pp.1436--1445, 2014 
\bibitem{JLCW02}
Jiang H.F., Lu H.J., Chin B., Wang W., XR-Tree:Indexing XML Data for 
Efficient Structural Joins. \emph{ICDE}, pp.253--264, 2003
\bibitem{KaME07}
Kakehi, K., Matsuzaki, K., Emoto, K.,
Efficient Parallel Tree Reductions on Distributed Memory Environments.
\emph{7th International Conference on Computational Science} (\emph{ICCS2007}), pp.601--608, 2007.
\bibitem{mbridges}
Kawamura K., Matsuzaki K., Dividing Huge XML Trees Using the m-bridge Technique over One-to-one orresponding Binary Trees. \emph{IPSJ Transaction on Programming}, pp.40--50, 2014. 
\bibitem{KrYa10}
Krulis, E., Yaghob, E., Efficient Implementation of 
XPath Processor on Multi-Core CPUs,  pp. 60--71, 
2010 
\bibitem{Mats07}
Matsuzaki, K., Parallel Programming with Tree Skeleton.
Ph.D. Thesis, The University of Tokyo, 2007.
\bibitem{MaMi15}
Matsuzaki, K., Miyazaki, R., 
Parallel Tree Accumulations on MapReduce.
\emph{International Journal of Parallel Programming}, online, 2015.
\bibitem{Mori13}
Morihata, A. Work Efficient Distributed-Memory Parallel Evaluation of XPath Queries,
In \emph{30th JSSST Conference Proceedings}, 2013. (in Japanese).
\bibitem{PLZC07}
Pan, Y., Lu, W., Zhang, Y., Chiu, K., A static 
load-balancing scheme for parallel XML parsing on 
multicore CPUs. \emph{IEEE International Symposium on 
Cluster Computing and the Grid}, Janeiro, pp. 
351--362, 2007 
\bibitem{SeAF05}
Sevilgen, F.E., Aluru, S., Futamura, N., Parallel Algorithms for Tree Accumulations,
\emph{Journal of Parallel and Distributed Computing}, vol.~65, no.~1, pp.85--93, 2005.
\bibitem{XML}
W3C, XML Tutorial, http://www.w3schools.com/xml/, 2010. 
\bibitem{XPath}
W3C, XML Path Language (XPath) 2.0 (Second 
Edition), http://www.w3.org/TR/xpath20/, 2010. 
\bibitem{WZYL08}
Wu, Y., Zhang, Q., Yu, Z., Li, J. A Hybrid Parallel 
Processing for XML Parsing and Schema Validation. 
\emph{The Markup Conference, Cluster Computing and the 
Grid, Seventh IEEE International Symposium}, pp. 
351--362, 2008. 
\bibitem{XMark}
XMark, XMark - An XML Benchmark Project, 
http://www.xml-benchmark.org/generator.html, 2010. 
\bibitem{ZhPC10}
Zhang, Y., Pan Y., Chiu K., A Parallel XPath Engine 
Based on Concurrent NFA Execution, \emph{IEEE 16th 
International Conference on Parallel and Distributed 
Systems}, pp. 314--321, 2010 
\end{thebibliography}
