\section{Implementing Data Partitioning with BaseX}
\label{sect:dpsimpl}

In this section, we describe our two implementations for data partitioning
strategy, namely the client-side implementation and the server-side
implementation, on top of BaseX.

Data partitioning is to split a given query into a prefix query and a suffix
query, e.g., from \texttt{$q_1$/$q_2$} to prefix $q_1$ and suffix $q_2$, and to
run the suffix query in parallel on each node of the result of the prefix query.
The results of suffix queries are concatenated in document order to form the 
final result.


Our implementations are Java programs that involve a BaseX client. They
spawn $P$ threads (usually P is no more than the number of physical cores) and 
create a connection to a BaseX server for each thread so
as to run multiple queries in parallel after a prefix query. Merging $P$ partial
results in the form of string is sequentially implemented. The main difference
between the client-side and the server-side implementations is the way how the results of prefix
queries are handled. In the rest of this section, we describe them by using
XM3(a) shown in Table~\ref{tab:dpsqueries} as a running example, assuming input
database to be named \Src{`xmark.xml'}.

\subsection{Client-side Implementation}

The client-side implementation is a simple implementation of data partitioning
strategy with database operations on BaseX. It sends the server a prefix query 
to be executed and the PRE values of matched nodes are returned. The
following XQuery expression is used for the prefix query of XM3(a).

\begin{lstlisting}
for $x in db:open(``xmark'')/site//open_auction
return db:node-pre($x)
\end{lstlisting}

Let this prefix query return sequence \Src{(2, 5, 42, 81, 109, 203)}. 
Letting $P = 3$, it is block-partitioned to \Src{(2, 5)}, \Src{(42,
81)}, and \Src{(109, 203)}, each of which is assigned to a thread. To avoid
repetitive ping-pong between a client and the server, we use the following
suffix query template:

\vspace{10mm}
\begin{lstlisting}[escapechar=\@]
for $x in @\Placeholder{sequence of PRE}@
return db:open-pre(``xmark'', $x)/bidder[last()]@\textrm{~,}@
\end{lstlisting}
where \Placeholder{sequence of PRE} is a placeholder to be replaced with a
concrete partition, e.g., \Src{(42, 81)}. Each thread instantiates this template
with its own partition and sends the server the instantiated query.


\subsection{Server-side Implementation}

A necessary task on the results of a prefix query is to block-partition them.
The client-side implementation simply processes it on the client side. In fact,
we can also implement it efficiently on the server side by utilizing BaseX's
features.

First, we prepare an in-memory database named \Src{``tmp''} and initialized with
\Src{<root> </root>}, which is a temporary database for storing the results of a
prefix query.  The prefix query is \texttt{/site//open\_auction} and it selects 
all \texttt{open\_auction} and return the PRE values of matched nodes. 
It is implemented as follows:

\begin{lstlisting}[escapechar=\@]
let $P := @\Placeholder{number of partitions}@
let $arr := array { for $x in db:open(``xmark'')/site//open_auction
                       db:node-pre($x) }
for $i in 1 to $P
return insert node element part { $block_part($i, $P, $arr) }
         as last into db:open('tmp')/root@\textrm{~,}@
\end{lstlisting}
where \Placeholder{number of partitions} denotes a placeholder to be replaced
with a concrete value of $P$ and \verb|$block_part($i, $P, $arr)| denotes the
\verb|$i|-th subarray of \verb|$P|-block partitioned \verb|$arr|. With the array
operations of extracting length and subarray, \verb|$block_part| is implemented
in logarithmic time.

In the example case used earlier, \Src{``tmp''} database results in the following:
\newpage
\begin{lstlisting}[escapechar=\@]
@$^1$@<root>
  @$^2$@<part>@$^3$@2 5</part>@$^4$@<part>@$^5$@42 81</part>@$^6$@<part>@$^7$@109 203</part>
@$^{\phantom{1}}$@</root>@\textrm{~,}@
\end{lstlisting}
where a left superscript denotes a PRE value. Note that its document structure
determines the PRE value of $i$th partition to be $2i+1$.

A suffix query is implemented with deserialization of a partition as follows:
\begin{lstlisting}[escapechar=\@]
for $x in ft:tokenize(db:open-pre(``tmp'', @\Placeholder{PRE of partition}@))
return db:open-pre('xmark', xs:integer($x))/bidder[last()])@\textrm{~,}@
\end{lstlisting}
where \Placeholder{PRE of partition} denotes a placeholder to be replaced with
the PRE value of a target partition.

In most case, the server-side implementation is more efficient because communication data
between clients and a server except for output is reduced to a constant size.


\begin{figure}[tbp]
	\centering
	\caption{List of XPath queries and their partitioning, where pre and suf
		mean prefix query and suffix query respectively}
	\label{tab:dpsqueries}
	\small
	\begin{tabular}{l|l}
		\hline
		Key & Query \\
		\hline
		XM1  & \verb|/site//*[name(.)="emailaddress" or name(.)="annotation" or| \\
		& \verb| name(.)="description"] |\\
		XM1(a) & pre = \verb|/site/*|, \\
		& suf = \verb|descendant-or-self::*[name(.)="emailaddress" or | \\
		& \verb|     name(.)="annotation" or name(.)="description"]| \\
		\hline
		XM2 & \verb|/site//incategory[./@category="category52"]/parent::item/@id| \\
		XM2(a) & pre = \verb|/site//incategory|, \quad \\
		& suf = \verb|self::*[./@category="category52"]/parent::item/@id| \\
		XM2(b) & pre = \verb|/site/*|, \quad  \\
		& suf = \verb|descendant-or-self::incategory[./@category="category52"]|\\
		& \verb|      /parent::item/@id| \\
		XM2(c) & pre = \verb|db:attribute("xmark10", "category52")|, \\
		& suf = \verb|parent::incategory[ancestor::site/parent::document-node()]| \\
		& \verb|      /parent::item/@id| \\
		\hline
		XM3 & \verb|/site//open_auction/bidder[last()]| \\
		XM3(a) & pre = \verb|/site//open_auction|, \quad suf = \verb|bidder[last()]| \\
		XM3(b) & pre = \verb|/site/*|, \quad \\
		& suf = \verb|descendant-or-self::open_auction/bidder[last()]| \\
		XM3(c) & pre = \verb|/site/open_auctions/open_auction|, \quad suf = \verb|bidder[last()]| \\
		\hline
		XM4 & \verb|/site/regions/*/item[./location="United States" and ./quantity > 0| \\
		& \verb| and ./payment="Creditcard" and ./description and ./name]| \\
		XM4(a) & pre = \verb|/site/regions/*|, \quad\\
		& suf = \verb|item[./location="United States" and ./quantity > 0 and | \\
		& \verb|     ./payment="Creditcard" and ./description and ./name]| \\
		XM4(b) & pre = \verb|/site/regions/*/item|, \quad \\
		& suf = \verb|self::*[./location="United States" and ./quantity > 0 and|  \\
		& \verb|     ./payment="Creditcard" and ./description and ./name]| \\
		XM4(c) & pre = \verb|db:text("xmark10", "Creditcard")/parent::payment|, \\
		& suf = \verb|parent::item[parent::*/parent::regions| \\
		& \verb|      /parent::site/parent::document-node()]| \\
		& \verb|     [location = "United States"][0.0 < quantity][description][name]| \\
		\hline
		XM5 & \verb|/site/open_auctions/open_auction/bidder/increase| \\
		XM5(a) & pre = \verb|/site/open_auctions/open_auction/bidder|, \quad suf = \verb|increase| \\
		XM5(b) & pre = \verb|/site/open_auctions/open_auction|, \quad suf = \verb|bidder/increase| \\
		\hline
		XM6 & \verb|/site/regions/*[name(.)="africa" or name(.)="asia"]| \\
		&  \verb|/item/description/parlist/listitem| \\
		XM6(a) & pre = \verb|/site/regions/*|, \quad \\
		& suf = \verb|self::*[name(.)="africa" or name(.)="asia"]|\\
		& \verb|     /item/description/parlist/listitem| \\
		XM6(b) & pre = \verb|/site/regions/*[name(.)="africa" or name(.)="asia"]/item|, \quad  \\
		& suf = \verb|description/parlist/listitem| \\
		\hline
		DBLP1 & \verb|/dblp/article/author|\\
		DBLP1(a) & pre = \verb|/dblp/article|,   suf = \verb|author|\\
		\hline
		DBLP2 & \verb|/dblp//title|\\
		DBLP2(a) & pre = \verb|/dblp/*|,  suf = \verb|self::*//title|\\
		\hline
	\end{tabular}
\end{figure}
