\newcommand{\Placeholder}[1]{$\langle\!\langle\mbox{\textrm{#1}}\rangle\!\rangle$}
\newcommand{\bfn}[1]{\textup{#1}}
\newcommand{\Src}[1]{\texttt{#1}}
\newcommand{\fn}[1]{\mathit{#1}}
\newcommand{\modify}[3]{{\underline{\sf{#1}}:} {\color{blue}{#2}} {\color{green}{\mbox{$\Rightarrow$}}} {\color{red}{#3}}}
\newcommand{\todo}[2]{{\underline{\textsf{#1}}:} {\color{red}{$\spadesuit$#2$\spadesuit$}}}
\newcommand{\hack}{{\color{red}{$\blacklozenge$}}}


\chapter{Parallelization Of XPath Queries on Top of BaseX}

On the topic of parallelelization of XPath queires, one practical and promising
approach was proposed by Bordawekar et al.~\cite{Bord10} in 2009. In this study,
three partitioning strategies were presented, i.e. data partitioning, query
partitiooning  and hybrid partitioing startegies,  making it possible to
parallelize XPath queries by partitioning an XPath query into subqueries and
evaluating them in parallel on XML trees.

However, since this study was based on an XSLT processing, it is thus not clear
to the following questions: \textit{(1) Whether and how can we apply their
partitioning strategies to XML database engines? (2) What speedup can we achieve
on large XML documents?}.

To answer the above two questions, we introduce our implementations on top of a
state-of-the-art XML database engine BaseX with two large XML documents sized 
1.1 GB and 1.85 GB by reviving and extending Bordawekar et al's study. We propose
three implementations on the base of the original idea from the paper and we also
extended our implementations in term of BaseX by exploiting its optimizations.
We experimentally demonstrate the performance on top of BaseX with two large 
XML documents. The experiment results proved that it is
possible to obtain significant speedups by simply rewriting queries into
subqueries and parallelizing the evaluation of them on top of an XML database
engine over gigabytes of XML documents, without need to modify source code of the engine.

%\input{basex/partitions}

\input{basex/basex}

\input{basex/dpsimpl}

\input{basex/qpsimpl}

\input{basex/optimization}

\input{basex/evaluation}

\input{basex/conclusion}
