% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments


There were many persons who provided me a lot of assistance with this work. 
Without their assistance, I could not finish this thesis. Therefore, 
I would like to give my sincere
gratitude to them, particularly the following professors, classmates, family
members, friends etc.

First and foremost, I would like to give my sincerest gratitude to my doctoral
supervisor Assoc. Prof. Kiminori Matsuzaki. It is my greatest honor to be his
first Ph.D. student. Associate Prof. Kiminori Matsuzaki is a very kind and amiable
person with the consistent solid support both on my Ph.D. research work and
daily life in Japan. I appreciate all his contributions of energetic enthusiasm,
immense knowledge and experience on research, insightful ideas, and generous
support, making my Ph.D. experience productive and fruitful. I am also thankful
to his excellent advice and examples he has provided as a successful computer
scientist and professor.

% Prof. Li, Jingzhao, who gave me great help in my daily life.

I would like to express sincere appreciation to Dr.Shigeyuki Sato for his great
help on my research work. I have quite often been enlightened by his very strict
attitude towards research work and setting such a good example for me.

I would like to think Assoc. Prof. Tomoharu Ugawa for his helpful advice 
on my research. I would like to thank Prof. Jingzhao Li, who assisted me 
with some job issues back in China. 

I would like to thank my wife WenJun Xie, my father Wenlin Hao, and my
mother Qinglin Zhu for their significant supports and encouragements.

I would like to thank the following friends: Onofre Call Ruiz, who was my 
classmate and lab mate. He gave me a great help in English learning and 
daily life. I would like to thank Naudia Patterson, who is an English 
teacher and assisted me with revising my thesis.

%I would like to thank my committee members, ..., for their valuable feedback
% throughout the project.
 

I would like to express sincere appreciation to Kochi University of Technology
for providing me such a great research opportunity.


% Last, ICR members, KUT faculty members, etc.
\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------


